### 2012-11-25 paper.tex
bump
added table for the poor results of decision tree on echocardiogram

Using an unpruned tree doesn't improve the results:
\begin{lstlisting}
J48 unpruned tree
pericardial-effusion = 0
|   epss <= 13100: 1 (76.62/1.95)
|   epss > 13100
|   |   epss <= 15600: 0 (2.19/0.16)
|   |   epss > 15600: 1 (2.19/0.03)
pericardial-effusion = 1: 1 (14.0)
\end{lstlisting}
Here, the existence of a pericardial effusion (fluid around the heart) is assumed to be a healthy characteristic, but it is not. Accordingly, the precision of the J48 decreases from 95\% to 88\%.

>>>>

Using an unpruned tree doesn't improve the results:
\begin{lstlisting}
J48 unpruned tree
pericardial-effusion = 0
|   epss <= 13100: 1 (76.62/1.95)
|   epss > 13100
|   |   epss <= 15600: 0 (2.19/0.16)
|   |   epss > 15600: 1 (2.19/0.03)
pericardial-effusion = 1: 1 (14.0)
\end{lstlisting}
Here, the decision tree assumes a pericardial effusion (fluid around the heart) to be a healthy characteristic, but it is not. Accordingly, the precision of the J48 decreases from 95\% to 88\%. Using a higher confidence factor instead of a totally unpruned tree has no effect on the quality or the classification distribution.

\paragraph{Other parameter}
Neither the laplace correctin to smooth the count of the leaves nor reduced error pruning has any effect on the quality of result. Without mdl correction the precision decreases a little to 91.9\%. Raising the minimum of instances per leaf has no effect either, which is no suprise since the data set is rather small. We couldn't get a better result with the J48 algorithm than to classify all patients to survive at least one year. The detailed accuracy for this simple, single-sided classification can be seen in table
\ref{tab:echo:dec:best}.

\begin{table*}[htb]\centering
    \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
        \toprule 
        \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure &  Class  \\ \midrule
               &  0       & 0       & 0         & 0      & 0         &  0      \\     
               &  1       & 1       & 0.959     & 1      & 0.979     &  1      \\     
Weighted Avg.  &  0.959   & 0.959   & 0.919     & 0.959  & 0.939     &         \\ \bottomrule
    \end{tabular*}
\caption{Decision Tree -- best achievable results} 
\label{tab:echo:dec:best}
\end{table*}
\FloatBarrier
